---
title: "writing_functions"
author: "Ruoxi Li"
date: "`r Sys.Date()`"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)
```

Set seed for reproducibility.

```{r}
set.seed(12345)
```

### Z score function

Z scores substract the mean and divide by the sd.

```{r}
x_vec=rnorm(20,mean=5,sd=.3)

```

Compute Z scores for 'x_vec'

```{r}
(x_vec-mean(x_vec))/sd(x_vec)
```

```{r}
z_score = function(x){
  
  if(!is.numeric(x)){
    stop("Argument should be numbers")
  } else if(length(x)<2){
    stop("You need at least 2 numbers to get z scores")
  }
  z = (x-mean(x))/sd(x)
  
  z
}
```

Check that this works.

```{r}
z_score(x=x_vec)
```

Keep checking...
```{r,error=TRUE}
z_score(x=3)

z_score(c("my","name","is","jeff"))

z_score(c(TRUE,TRUE,FALSE,TRUE))

z_score(iris)
```


### Multiple outputs

Write a function that returns the mean and sd from a sample of numbers.
```{r}
mean_and_sd = function(x){
  
  if(!is.numeric(x)){
    stop("Argument should be numbers")
  } else if(length(x)<2){
    stop("You need at least 2 numbers to get z scores")
  }
  
  mean_x =mean(x)
  sd_x = sd(x)
  
  tibble(
    mean=mean_x,
    sd=sd_x
  )
}
```

Double check I did this right

```{r}
mean_and_sd(x_vec)
```  

###  Start getting means and sds

```{r}

x_vec = rnorm(n=30,mean=5,sd=.5)

 
  tibble(
    mean=mean(x_vec),
    sd=sd(x_vec)
  )
```

Let's write a function that uses `n`, a true mean, and true sd as inputs

```{r}
sim_mean_sd = function(n_obs,mu=5,sigma=1){
  x_vec = rnorm(n=n_obs,mean=mu,sd=sigma)

 
  tibble(
    mean=mean(x_vec),
    sd=sd(x_vec)
  )
}

sim_mean_sd(n_obs = 3000, mu=50)
#this will overwright the default value

sim_mean_sd(12,24,4)
```

